Stability in human interaction networks: sector relative sizes, prominence of topological measures and time activity statistics.

### 2015-05-05 paper.tex
melhorado layout
melhorada escrita de algumas partes e as medidas ao longo do mes

@@

\begin{table}
	\caption{Example of activity percentages along the hours of the day. Higher activity was observed between noon and 6pm, followed by the time period between 6pm and midnight. Around 2/3 of the whole activity takes place from noon to midnight. Nevertheless, the activity peak occurs around midday, with a slight skew toward one hour before noon.}
	\footnotesize
	\input{tables/tabHoursCPP_}
\label{tab:hin}
\end{table}

\FloatBarrier
\begin{table}
	\caption{Example of activity percentages along the days of the week. Higher activity was observed during weekdays, with a decrease of activity on weekends of at least one third and two thirds in extreme cases.}
\begin{center}
    \begin{tabular}{ | l |  c | c | c | c | c |   c | c |}
        \hline
        & Mon & Tue & Wed & Thu & Fri & Sat & Sun  \\ \hline
	\input{tables/tabWeekdays}
    \end{tabular}
\end{center}
\label{tab:win}
\end{table}
\begin{table}
	\caption{No significant variation of activity in the days along the month was observed. One cannot point much more than a - probably not statistically relevant - tendency of first and second weeks to be more active. The most important trait seems to be homogeneity.}
	\footnotesize
	\input{tables/tabMonthdaysCPP}
\label{tab:min}
\end{table}

@@

\subsection{Scalable fat-tail structure: constancy of membership fractions in the Erd\"os sectors}\label{subsec:pih}

>>>>

As expected, a positive correlation was found in all $Var(z)$, $S(z)$ and $\delta(z)$ dispersion measures (as can be noticed in Supporting Information) and $\delta(z)$ was preferred in the discussion of results.

@@

\begin{table}
	\caption{Activity percentages along the hours of the day for the CPP list. Nearly identical distributions are found on other lists as exposed in Supporting Information. Higher activity was observed between noon and 6pm, followed by the time period between 6pm and midnight. Around 2/3 of the whole activity takes place from noon to midnight. Nevertheless, the activity peak occurs around midday, with a slight skew toward one hour before noon.}
	\footnotesize
	\input{tables/tabHoursCPP_}
\label{tab:hin}
\end{table}

\FloatBarrier
\begin{table}
	\caption{Activity percentages along the days of the week for all four example lists. Higher activity was observed during weekdays, with a decrease of activity on weekends of at least one third and two thirds in extreme cases.}
\begin{center}
    \begin{tabular}{ | l |  c | c | c | c | c |   c | c |}
        \hline
        & Mon & Tue & Wed & Thu & Fri & Sat & Sun  \\ \hline
	\input{tables/tabWeekdays}
    \end{tabular}
\end{center}
\label{tab:win}
\end{table}
\begin{table}
	\caption{Activity in the days along the month for MET list. Nearly identical distributions are found on other lists as exposed in Supporting Information. Although slightly higher activity rates are found in the beginning of the month, the most important trait seems to be the homogeneity made explicit by the high circular dispersion on Table~\ref{tab:circ}.}
	\footnotesize
	\input{tables/tabMonthdaysMET}
\label{tab:min}
\end{table}

@@

\vspace*{1cm}
\subsection{Scalable fat-tail structure: constancy of membership fractions in the Erd\"os sectors}\label{subsec:pih}
